The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-22 paper/sections/methods.tex
finally multipart projection

Attempting to use $\Pmatxi$ in~\refeq{shapematch} on a per-part basis is problematic as it can become ill-posed, especially for planar boundary representations. 
To alleviate this problem we invoke the \emph{hierarchical ordering principle}, which argues that the behavior of a system is typically 
dominated by lower order effects~\cite{li2006regularities}.

>>>>

Attempting to use $\Pmatxi$ in~\refeq{shapematch} on a per-part basis is problematic as it can become ill-posed, especially for planar boundary representations. 
To alleviate this problem we invoke the \emph{hierarchical ordering principle}, which argues that the behavior of a system is typically 
dominated by lower order effects~\cite{li2006regularities}. 
Mechanically, this principle suggests that the amount of motion modelled by increasingly high-order polynomials is decreasing. 
This implies that we can achieve acceptable shape matching results by performing shape matching hierarchically -- starting with the constant term and then 
fitting the remaining deformation with progressively higher-order deformations.

For a given part, $\prt_i$, with associated origin $\bar{\refX}_j$ we first estimate the constant term, $\tr_i$ as the centroid of all parts associated with $\bar{X}_j$.
We next fit the linear part of the deformation by performing linear shape matching to $\prt_i$. 
This can be repeated for polynomials of arbitrary high order, for instance here we apply this approach to quadratic shape matching:

\begin{equation*}
    \begin{split}
        \tr_i  & = \sum_{\prt_k \in \bar{\refX}_j} \mathbbm{1}^T\wt_k \samp{\Jnurbs}_k\vc{q}_k \\
        \vc{c}_i^1 & = \left(\samp{\Pmat^1}^T\wt_i\samp{\Pmat^1}\right)^{-1}\samp{\Pmat^1}^T\wt_i\left(\samp{\Jnurbs}_i\vc{q}_i-\mathbbm{1}\tr_i\right)\\
        \vc{c}_i^2 & = \left(\samp{\Pmat^2}^T\wt_i\samp{\Pmat^2}\right)^{-1}\samp{\Pmat^2}^T\wt_i\left(\samp{\Jnurbs}_i\vc{q}_i-\samp{\Pmat^1}\vc{c}_i^1 - \mathbbm{1}\tr_i\right)
    \end{split},
    \label{eq:hfit} 
\end{equation*} where $\Pmat^l$ contains only the monomial basis of order $l$,  $\samp{\Pmat^1}$ is the stacked evaluation of this matrix at $n$ quadrature points and $\vc{c}^l_i$ are the corresponding coefficients. 
Finally, $\wt_i$ is the diagonal integration weight matrix and $\mathbbm{1}\in\real^{3n\times3}$ is a matrix of stacked $3\times3$ identity matrices -- one for each quadrature point.

Coupling via the deformation origins ensures our method will reproduce rigid and linear deformations in regions around these points, while higher order 
terms help compensate for more local deformations.

\dave{should have done Chebyshev shape matching to ensure higher order terms are orthogonal which would gaurantee exact reconstruction}
